Report: Illustration Results

### 2023-07-29 IllustrationResultsRenderReport.Rmd
internal feedback
feedback lfb

varNames %>%
  filter(
    pca != 0,
    varNam %in% c(varNamS123PCA, varNamS1PCA, varNamS2PCA, varNamS3PCA)
  ) %>%
  mutate(
    contactSpecific = recode(
      .$contactSpecific,
      `-1` = "No Interaction Only",
      `0` = "unspecific",
      `1` = "Interaction Only"
    ),
    study1 = ifelse(!is.na(studyS1), 1, 0),
    study2 = ifelse(!is.na(studyS2), 1, 0),
    study3 = ifelse(!is.na(studyS3), 1, 0)
  ) %>% 
  select(varNam, varGroup, contactSpecific, study1, study2, study3) %>%
  filter(study1 == 1 & study2 == 1 & study3 == 1) %>%
  group_by(varGroup, varNam, contactSpecific, study1, study2, study3) %>%
  summarise(n = n()) %>%
  pivot_wider(names_from = c("varGroup", "varNam", "study1", "study2", "study3"), values_from = n, names_sep=" - ") %>%
  ungroup %>%
  t %>%
  as.data.frame %>%
  janitor::row_to_names(1) %>%
  replace(is.na(.), 0) %>%
  tibble::rownames_to_column(., var = "variable") %>%
  separate(variable, c("concept", "variable", "study1", "study2", "study3"), " - ") %>%
  mutate(across(c(study1, study2, study3), as.numeric)) %>%
  #select(-study1, -study2, -study3) %>%
  arrange(concept, unspecific, `Interaction Only`) %>% 
  mutate_all(~recode(.x, `0`="", ` 1`="X")) %>%
  relocate(starts_with("study"), .after = last_col()) %>%
  rename_with(., ~ gsub("study", "Study ", .x, fixed = TRUE)) %>%
  kbl(.,
      escape = FALSE,
      booktabs = T,
      align = c("l", "l", rep("c", ncol(.)-2)),
      digits=2,
      caption = "Variables by Interaction Types and Study Availability") %>%
  add_header_above(c(" " = 2, "Contact Type" = 2, "Study Availability" = 3)) %>%
  kable_classic(
    full_width = F,
    lightable_options = "hover",
    html_font = "Cambria"
  )
```

@@

## CLuster Performance

@@

## CLuster Interpretation

>>>>

varNames %>%
  filter(
    pca != 0,
    varNam %in% c(varNamS123PCA, varNamS1PCA, varNamS2PCA, varNamS3PCA)
  ) %>%
  mutate(
    contactSpecific = recode(
      .$contactSpecific,
      `-1` = "No Interaction Only",
      `0` = "unspecific",
      `1` = "Interaction Only"
    ),
    study1 = ifelse(!is.na(studyS1), 1, 0),
    study2 = ifelse(!is.na(studyS2), 1, 0),
    study3 = ifelse(!is.na(studyS3), 1, 0)
  ) %>% 
  select(varNam, question, varGroup, contactSpecific, study1, study2, study3) %>%
  filter(study1 == 1 & study2 == 1 & study3 == 1) %>%
  group_by(varGroup, varNam, question, contactSpecific, study1, study2, study3) %>%
  summarise(n = n()) %>%
  pivot_wider(names_from = c("varNam", "question", "varGroup", "study1", "study2", "study3"), values_from = n, names_sep=" - ") %>%
  ungroup %>%
  t %>%
  as.data.frame %>%
  janitor::row_to_names(1) %>%
  replace(is.na(.), 0) %>%
  tibble::rownames_to_column(., var = "variable") %>%
  separate(variable, c("Variable", "Question", "Aspect", "study1", "study2", "study3"), " - ") %>%
  mutate(across(c(study1, study2, study3), as.numeric)) %>%
  select(-study1, -study2, -study3) %>%
  arrange(`Interaction Only`, Variable) %>% 
  mutate(ESM = 1) %>%
  mutate_all(~recode(.x, `0`="", ` 1`="✔")) %>%
  relocate(starts_with("ESM"), .after = "Aspect") %>%
  # relocate(starts_with("study"), .after = last_col()) %>%
  # rename_with(., ~ gsub("study", "Study ", .x, fixed = TRUE)) %>%
  kbl(.,
      escape = FALSE,
      booktabs = T,
      align = c("l", "l", "l", rep("c", ncol(.)-3)),
      digits=2,
      caption = "Variables by Interaction Types and Study Availability") %>%
  add_header_above(c(" " = 4, "Contact Specific" = 2)) %>%
  kable_classic(
    full_width = F,
    lightable_options = "hover",
    html_font = "Cambria"
  )
```

@@

## Cluster Performance

@@

## Cluster Interpretation

### 2023-07-29 latex-results/07ClusterEvaluationInterpretation.tex
feedback lfb

Finally, we can also assess the clusters across other individual
difference variables \citep[e.g.,][]{monden2022}. This out-of-feature
comparison allows us to check for data artifacts, as well as check
whether the developmental clusters are associated with important social
markers and individual differences. To illustrate artifact checks, we
added the number of ESM measurements into the comparison and find that
the participants in the deterioration cluster (cluster 2) on average
completed slightly more ESM surveys in general and reported on more
intergroup interactions in particular (see \(n\) in
\fgrref[B]{fig:clusterFeatVar}). In our data exclusion procedures, we
ensured that the general time frame and completion rates are similar for
all participants and indeed the numbers in ESM measurements generally
are largely similar (e.g., see \(n\) for well-being and outgroup
attitudes). However, the difference in the reported number of
interactions might indicate either a clustering artifact or a meaningful
difference. The higher average number of interactions in cluster 2
could, for example, indicate a clustering artifact if variances are more
inflated due to the larger samples \citep{kogan2006}. At the same time,
however, the difference in the number of experienced interactions might
also indicate a meaningful difference, where the deteriorating cluster
(cluster 2) on average reported more outgroup interactions, but these
interactions were less voluntary, less meaningful, and less positive.
Such a finding is in line with past research highlighting the role of
negative intergroup interactions in explaining intergroup relations
\citep[e.g.,][]{Barlow2012, Prati2021, Graf2014}.

@@

This cluster separation, then, has a number of empirical and practical
applications. Firstly, the clusters are descriptive. With tens of
variables, hundreds of participants, and thousands of measurements,
singular descriptive statistics are often not able to capture the
complex patterns that describe the data set. The feature-based
clustering offers some direct insight into the complexity within the
data set. In our empirical example, we, for example, see that
participants are meaningfully distinguished by a combination of high
(vs.~low) central tendency, variability, and linear trend. Secondly, the
clusters identify important groups. The adaptive and deteriorating
groups offer starting points for empirical exploration as well as
practical interventions. Researchers can start probing what exactly
distinguishes the two groups further and generate new bottom-up
hypotheses. Practitioners in the resettlement field can use the group
separation to identify individuals in need of assistance and can explore
contextual factors that might contribute to the difficulties some might
face. Thirdly, the feature-based approach is flexible and meaningful. We
were able to use a wide range of time series features that have been
central in the ESM literature and were able to use them directly to
identify meaningful groups. For our empirical illustration we, among
others for example, chose to focus on whether participants differed in
their average well-being (i.e., \textit{median}), how much their
well-being would vary over time (i.e, \textit{MAD}), and whether their
well-being would on average increase or decrease over time (i.e.,
\textit{linear trend}). Alternatively, for others cyclical patterns
might be more important --- for example, whether well-being was higher
on weekends. Importantly, in any case, we did not need to translate
these dynamic features into probabilistic inference models (e.g., VAR
models) to cluster the participants.

>>>>

Finally, we can also assess the clusters across other individual
difference variables \citep[e.g.,][]{monden2022}. This out-of-feature
comparison allows us to check for data artifacts, as well as check
whether the developmental clusters are associated with important social
markers and individual differences. To illustrate artifact checks, we
added the number of ESM measurements into the comparison and find that
the participants in the deterioration cluster (cluster 2) on average
completed slightly more ESM surveys in general and reported on more
intergroup interactions in particular (see \(n\) in
\fgrref[B]{fig:clusterFeatVar}). In our data exclusion procedures, we
ensured that the general time frame and completion rates are similar for
all participants and indeed the numbers in ESM measurements generally
are largely similar (e.g., see \(n\) for well-being and outgroup
attitudes). However, the difference in the reported number of
interactions might indicate either a clustering artifact or a meaningful
difference. The higher average number of interactions in cluster 2
could, for example, indicate a clustering artifact if variances are more
inflated due to the larger samples \citep{kogan2006}. In our case this
seems less likely because one out of four variables did not differ in
terms of the MAD (see \fgrref{fig:cluster_comparison_mad}). At the same
time, however, the difference in the number of experienced interactions
might also indicate a meaningful difference, where the deteriorating
cluster (cluster 2) on average reported more outgroup interactions
(\(difference\) = 1.028, \(t\)(150.83) = 7.50, \(p\) \textless{} .001,
\(95%CI [0.76, 1.30]), but these interactions were less voluntary (
\)difference\$ = -1.04, \(t\)(108.89) = -7.71, \(p\) \textless{} .001,
\(95%CI [-1.31, -0.77]), less meaningful (
\)difference\$ = -1.003, \(t\)(136.40) = -7.16, \(p\) \textless{} .001,
\(95%CI [-1.28, -0.73]), and less positive (
\)difference\$ = -1.38, \(t\)(152.31) = -11.94, \(p\) \textless{} .001,
\$95\%CI {[}-1.61, -1.15{]}). Such a finding is in line with past
research highlighting the role of negative intergroup interactions in
explaining intergroup relations
\citep[e.g.,][]{Barlow2012, Prati2021, Graf2014}.

\begin{figure}[!ht] %hbtp
  \caption{Cluster comparison of Median Absolute Deviation for all variables}
  \label{fig:cluster_comparison_mad}
  \centering\includegraphics[width=\textwidth]{figures/feature_comparison_mad.pdf}
\end{figure}

@@

This cluster separation, then, has a number of empirical and practical
applications. Firstly, the clusters are descriptive. With tens of
variables, hundreds of participants, and thousands of measurements,
singular descriptive statistics are often not able to capture the
complex patterns that describe the data set. The feature-based
clustering offers some direct insight into the complexity within the
data set. In our empirical example, we, for example, see that
participants are meaningfully distinguished by a combination of high
(vs.~low) central tendency, variability, and linear trend. Secondly, the
clusters identify important groups. The adaptive and deteriorating
groups offer starting points for empirical exploration as well as
practical interventions. Researchers can start probing what exactly
distinguishes the two groups further and generate new bottom-up
hypotheses. Practitioners in the resettlement field can use the group
separation to identify individuals in need of assistance and can explore
contextual factors that might contribute to the difficulties some might
face. In our illustration we, for example, found that participants in
the deteriorating cluster (cluster 2) reported less need fulfilling
interactions over time. Thirdly, the feature-based approach is flexible
and meaningful. We were able to use a wide range of time series features
that have been central in the ESM literature and were able to use them
directly to identify meaningful groups. For our empirical illustration
we, among others for example, chose to focus on whether participants
differed in their average well-being (i.e., \textit{median}), how much
their well-being would vary over time (i.e, \textit{MAD}), and whether
their well-being would on average increase or decrease over time (i.e.,
\textit{linear trend}). Alternatively, for others cyclical patterns
might be more important --- for example, whether well-being was higher
on weekends. Importantly, in any case, we did not need to translate
these dynamic features into probabilistic inference models (e.g., VAR
models) to cluster the participants.

### 2023-07-29 sections/02InputVariables.Rmd
feedback lfb

@@

allMlCor <-
  MlCorMat(
    data = dtAll,
    id = "ID",
    selection = c(
      "InteractionContextAccidental", 
      "InteractionContextvoluntary", 
      "InteractionContextCooperative",
      "InteractionContextRepresentativeNL",
      "qualityMeaning",
      "qualityOverall", 
      "KeyNeedFulfillment", 
      "KeyNeedDueToPartner", 
      "AttitudesPartner",
      "DaytimeNeedFulfillment",
      "AttitudesDutch",
      "exWB"
    ),
    labels = c(
      "Int: Accidental", 
      "Int: Voluntary", 
      "Int: Cooperative",
      "Int: Representative",
      "Int: Meaningful",
      "Int: Quality", 
      "Core Need", 
      "Core Need Due to Partner", 
      "Attitude Partner",
      "Daytime Core Need",
      "Outgroup Attitude",
      "Well-being"
    )
  )
```

```{r}
# Sample Descriptives Table --- wider version
allMlCor %>%
  t %>%
  as.data.frame %>%
  kbl(.,
      format = "latex",
      caption = "Correlation Table and Descriptive Statistics",
      label = "descrWide",
      booktabs = TRUE,
      align = c("l", rep("c", ncol(.) - 1))) %>%
  kable_classic() %>%
  add_header_above(
    .,
    c(
      "",
      "Correlations" = ncol(allMlCor),
      "Descriptives" = nrow(allMlCor) - ncol(allMlCor)
    )
  ) %>%
  footnote(
    general = c(
      "Upper triangle: Between-person correlations;",
      "Lower triangle: Within-person correlations;",
      "*** p < .001, ** p < .01,  * p < .05"
    )
  ) %>%
  kable_styling(latex_options = "scale_down") %>%
  gsub("\\begin{table}", "\\begin{sidewaystable}\n\\centering", ., fixed = TRUE) %>%
  gsub("\\end{table}", "\\end{sidewaystable}", ., fixed = TRUE) %>%
  save_kable("Tables/descrWide.tex")
```

@@

# Sample Descriptives Table --- longer version
allMlCor %>%
  as.data.frame %>%
  kbl(.,
      format = "latex",
      caption = "Correlation Table and Descriptive Statistics",
      booktabs = TRUE,
      align = "c", #c("l", rep("c", ncol(.) - 1)),
      escape = FALSE,
      label = "descrLong",
      col.names = c(
        #"",
        "\\makecell{Int: \\\\ Accidental}",
        "\\makecell{Int: \\\\ Voluntary}", 
        "\\makecell{Int: \\\\ Cooperative}",
        "\\makecell{Int: \\\\ Representative}",
        "\\makecell{Int: \\\\ Meaningful}",
        "\\makecell{Int: \\\\ Quality}", 
        "Core Need", 
        "\\makecell{Core Need \\\\ Due to Partner}", 
        "\\makecell{Attitude \\\\ Partner}",
        "\\makecell{Daytime \\\\ Core Need}",
        "\\makecell{Outgroup \\\\ Attitude}",
        "Well-being"
      )) %>%
  kable_classic() %>%
  pack_rows("Correlations", 1, ncol(allMlCor)) %>%
  pack_rows("Descriptives", ncol(allMlCor)+1, nrow(allMlCor)) %>%
  footnote(
    general = c(
      '"Int." = interaction.',
      'Upper triangle: Between-person correlations;',
      'Lower triangle: Within-person correlations;',
      '*** p < .001, ** p < .01,  * p < .05'
    )
  ) %>%
  kable_styling(latex_options = "scale_down") %>%
  gsub("\\begin{table}", "\\begin{sidewaystable*}[!hbtp]\n\\centering", ., fixed = TRUE) %>%
  gsub("\\end{table}", "\\end{sidewaystable*}", ., fixed = TRUE) %>%
  save_kable("Tables/descrLong.tex")
```

>>>>

```{r}

varNames %>%
  filter(
    pca != 0,
    varNam %in% c(varNamS123PCA, varNamS1PCA, varNamS2PCA, varNamS3PCA)
  ) %>%
  mutate(
    contactSpecific = recode(
      .$contactSpecific,
      `-1` = "No Interaction Only",
      `0` = "unspecific",
      `1` = "Interaction Only"
    ),
    study1 = ifelse(!is.na(studyS1), 1, 0),
    study2 = ifelse(!is.na(studyS2), 1, 0),
    study3 = ifelse(!is.na(studyS3), 1, 0)
  ) %>% 
  select(varNam, question, varGroup, contactSpecific, study1, study2, study3) %>%
  filter(study1 == 1 & study2 == 1 & study3 == 1) %>%
  group_by(varGroup, varNam, question, contactSpecific, study1, study2, study3) %>%
  summarise(n = n()) %>%
  pivot_wider(names_from = c("varNam", "question", "varGroup", "study1", "study2", "study3"), values_from = n, names_sep=" - ") %>%
  ungroup %>%
  t %>%
  as.data.frame %>%
  janitor::row_to_names(1) %>%
  replace(is.na(.), 0) %>%
  tibble::rownames_to_column(., var = "variable") %>%
  separate(variable, c("Variable", "Question", "Aspect", "study1", "study2", "study3"), " - ") %>%
  mutate(across(c(study1, study2, study3), as.numeric)) %>%
  select(-study1, -study2, -study3) %>%
  arrange(`Interaction Only`, Variable) %>% 
  mutate(ESM = 1) %>%
  mutate_all(~recode(.x, `0`="", ` 1`="✔")) %>%
  relocate(starts_with("ESM"), .after = "Aspect") %>%
  # relocate(starts_with("study"), .after = last_col()) %>%
  # rename_with(., ~ gsub("study", "Study ", .x, fixed = TRUE)) %>%
  kbl(.,
      escape = FALSE,
      booktabs = T,
      align = c("l", "l", "l", rep("c", ncol(.)-3)),
      digits = 2,
      format = "latex",
      label = "var_selection",
      caption = "Variable Selection") %>%
  add_header_above(c(" " = 4, "Contact Specific" = 2)) %>%
  kable_styling(latex_options = "scale_down") %>%
  gsub("\\begin{table}", "\\begin{sidewaystable*}[!hbtp]\n\\centering", ., fixed = TRUE) %>%
  gsub("\\end{table}", "\\end{sidewaystable*}", ., fixed = TRUE) %>%
  save_kable("tables/var_selection.tex")

```

\input{tables/var_selection}

@@

allMlCor <-
  MlCorMat(
    data = dtAll,
    id = "ID",
    selection = c(
      "InteractionContextAccidental", 
      "InteractionContextvoluntary", 
      "InteractionContextCooperative",
      "InteractionContextRepresentativeNL",
      "qualityMeaning",
      "qualityOverall", 
      "KeyNeedFulfillment", 
      "KeyNeedDueToPartner", 
      "AttitudesPartner",
      "DaytimeNeedFulfillment",
      "AttitudesDutch",
      "exWB"
    ),
    labels = c(
      "Int: Accidental", 
      "Int: Voluntary", 
      "Int: Cooperative",
      "Int: Representative",
      "Int: Meaningful",
      "Int: Quality", 
      "Int: Need Fulfillment", 
      "Int: Need Fulfillment Partner", 
      "Attitude Partner",
      "Daytime Need Fulfillment",
      "Outgroup Attitude",
      "Well-being"
    )
  )
```

```{r}
# Sample Descriptives Table --- wider version
allMlCor %>%
  t %>%
  as.data.frame %>%
  kbl(.,
      format = "latex",
      caption = "Correlation Table and Descriptive Statistics",
      label = "descrWide",
      booktabs = TRUE,
      align = c("l", rep("c", ncol(.) - 1))) %>%
  kable_classic() %>%
  add_header_above(
    .,
    c(
      "",
      "Correlations" = ncol(allMlCor),
      "Descriptives" = nrow(allMlCor) - ncol(allMlCor)
    )
  ) %>%
  footnote(
    general = c(
      "Upper triangle: Between-person correlations;",
      "Lower triangle: Within-person correlations;",
      "*** p < .001, ** p < .01,  * p < .05"
    )
  ) %>%
  kable_styling(latex_options = "scale_down") %>%
  gsub("\\begin{table}", "\\begin{sidewaystable}\n\\centering", ., fixed = TRUE) %>%
  gsub("\\end{table}", "\\end{sidewaystable}", ., fixed = TRUE) %>%
  save_kable("tables/descrWide.tex")
```

@@

# Sample Descriptives Table --- longer version
allMlCor %>%
  as.data.frame %>%
  kbl(.,
      format = "latex",
      caption = "Correlation Table and Descriptive Statistics",
      booktabs = TRUE,
      align = "c", #c("l", rep("c", ncol(.) - 1)),
      escape = FALSE,
      label = "descrLong",
      col.names = c(
        #"",
        "\\makecell{Int: \\\\ Accidental}",
        "\\makecell{Int: \\\\ Voluntary}", 
        "\\makecell{Int: \\\\ Cooperative}",
        "\\makecell{Int: \\\\ Representative}",
        "\\makecell{Int: \\\\ Meaningful}",
        "\\makecell{Int: \\\\ Quality}", 
        "\\makecell{Int: \\\\ Need Fulfil.}", 
        "\\makecell{Int: \\\\ Need Fulfil. Partner}", 
        "\\makecell{Attitude \\\\ Partner}",
        "\\makecell{Daytime \\\\ Core Need}",
        "\\makecell{Outgroup \\\\ Attitude}",
        "Well-being"
      )) %>%
  kable_classic() %>%
  pack_rows("Correlations", 1, ncol(allMlCor)) %>%
  pack_rows("Descriptives", ncol(allMlCor)+1, nrow(allMlCor)) %>%
  footnote(
    general = c(
      '"Int." = interaction.',
      'Upper triangle: Between-person correlations;',
      'Lower triangle: Within-person correlations;',
      '*** p < .001, ** p < .01,  * p < .05'
    )
  ) %>%
  kable_styling(latex_options = "scale_down") %>%
  gsub("\\begin{table}", "\\begin{sidewaystable*}[!hbtp]\n\\centering", ., fixed = TRUE) %>%
  gsub("\\end{table}", "\\end{sidewaystable*}", ., fixed = TRUE) %>%
  save_kable("tables/descrLong.tex")
```

### 2023-07-29 sections/07ClusterEvaluationInterpretation.Rmd
feedback lfb

Finally, we can also assess the clusters across other individual difference variables \citep[e.g.,][]{monden2022}. This out-of-feature comparison allows us to check for data artifacts, as well as check whether the developmental clusters are associated with important social markers and individual differences. To illustrate artifact checks, we added the number of ESM measurements into the comparison and find that the participants in the deterioration cluster (cluster 2) on average completed slightly more ESM surveys in general and reported on more intergroup interactions in particular (see $n$ in \fgrref[B]{fig:clusterFeatVar}). In our data exclusion procedures, we ensured that the general time frame and completion rates are similar for all participants and indeed the numbers in ESM measurements generally are largely similar (e.g., see $n$ for well-being and outgroup attitudes). However, the difference in the reported number of interactions might indicate either a clustering artifact or a meaningful difference. The higher average number of interactions in cluster 2 could, for example, indicate a clustering artifact if variances are more inflated due to the larger samples \citep{kogan2006}. At the same time, however, the difference in the number of experienced interactions might also indicate a meaningful difference, where the deteriorating cluster (cluster 2) on average reported more outgroup interactions, but these interactions were less voluntary, less meaningful, and less positive. Such a finding is in line with past research highlighting the role of negative intergroup interactions in explaining intergroup relations \citep[e.g.,][]{Barlow2012, Prati2021, Graf2014}.

This cluster separation, then, has a number of empirical and practical applications. Firstly, the clusters are descriptive. With tens of variables, hundreds of participants, and thousands of measurements, singular descriptive statistics are often not able to capture the complex patterns that describe the data set. The feature-based clustering offers some direct insight into the complexity within the data set. In our empirical example, we, for example, see that participants are meaningfully distinguished by a combination of high (vs. low) central tendency, variability, and linear trend. Secondly, the clusters identify important groups. The adaptive and deteriorating groups offer starting points for empirical exploration as well as practical interventions. Researchers can start probing what exactly distinguishes the two groups further and generate new bottom-up hypotheses. Practitioners in the resettlement field can use the group separation to identify individuals in need of assistance and can explore contextual factors that might contribute to the difficulties some might face. Thirdly, the feature-based approach is flexible and meaningful. We were able to use a wide range of time series features that have been central in the ESM literature and were able to use them directly to identify meaningful groups. For our empirical illustration we, among others for example, chose to focus on whether participants differed in their average well-being (i.e., \textit{median}), how much their well-being would vary over time (i.e, \textit{MAD}), and whether their well-being would on average increase or decrease over time (i.e., \textit{linear trend}). Alternatively, for others cyclical patterns might be more important --- for example, whether well-being was higher on weekends. Importantly, in any case, we did not need to translate these dynamic features into probabilistic inference models (e.g., VAR models) to cluster the participants.

@@

>>>>

@@

```{r}
#| label: formal cluster comparison
#| echo: false

raw_feat_clust <- data.frame(ID = as.numeric(names(kmeansOut$cluster)), cluster = kmeansOut$cluster) %>%
  merge(., z_data) %>%
  merge(., validationFeature)

concepts_and_feature <- str_match(colnames(raw_feat_clust), "(.*)_(.*)")
concepts <- na.omit(unique(concepts_and_feature[, 2]))
ts_features <- na.omit(unique(concepts_and_feature[, 3]))

feat_t_test <- function(df, cluster_var, concept, ts_feature) {
  column_name <- paste0(concept, "_", ts_feature)

  group1 <- df[df[[cluster_var]] == unique(df[[cluster_var]])[1], column_name]
  group2 <- df[df[[cluster_var]] == unique(df[[cluster_var]])[2], column_name]

  t.test(group1, group2)
}

results <- list()
for (feature in ts_features) {
  for (concept in concepts) {
    results[[feature]][[concept]] <- feat_t_test(raw_feat_clust, "cluster", concept, feature)
  }
}

results$ar01$AttitudesDutch$conf.int

results_df <- data.frame(concept = character(),
                         feature = character(),
                         difference = numeric(),
                         df = numeric(),
                         t_value = numeric(),
                         p_value = numeric(),
                         lwr = numeric(),
                         upr = numeric(),
                         stringsAsFactors = FALSE)

for (feature in ts_features) {
  for (concept in concepts) {
    # Run t-test
    test_result <- results[[feature]][[concept]]

    # Extract required values from t-test result
    difference <- test_result$estimate[1] - test_result$estimate[2]  # difference between group means
    t_value <- test_result$statistic  # t-value
    df <- test_result$parameter  # df
    p_value <- test_result$p.value  # p-value
    lwr <- test_result$conf.int[1] # lower CI
    upr <- test_result$conf.int[2] # upper CI

    # Add a row to the results dataframe
    results_df <- rbind(results_df, data.frame(concept = concept,
                                               feature = feature,
                                               difference = difference,
                                               t_value = t_value,
                                               df = df,
                                               p_value = p_value,
                                               lwr = lwr,
                                               upr = upr,
                                               stringsAsFactors = FALSE))
  }
}

results_df <- results_df %>%
      mutate(star = ifelse(p_value < 0.001, "***", ifelse(p_value < 0.01, "**", ifelse(p_value < 0.05, "*", ""))))

feature_plot_list <- list()

library(forestplot)
for (feature in unique(results_df$feature)) {
  # Subset the data for the current feature
  feature_data <- results_df[results_df$feature == feature, ]

  # Create a matrix for the forestplot function
  plot_matrix <- rbind(c("", "Difference", "Lower CI", "Upper CI"),
                       cbind(feature_data$concept,
                             feature_data$difference,
                             feature_data$lwr,
                             feature_data$upr))

  # Create the forest plot
  feature_plot_list[[feature]] <- forestplot::forestplot(labeltext = plot_matrix[, 1], 
             mean = as.numeric(plot_matrix[, 2]),
             lower = as.numeric(plot_matrix[, 3]),
             upper = as.numeric(plot_matrix[, 4]),
             xlab = "Difference",
             title = paste0("Forest plot for ", feature))
}

concept_plot_list <- list()
for (concept in unique(results_df$concept)) {
  # Subset the data for the current feature
  concept_data <- results_df[results_df$concept == concept, ]

  # Create a matrix for the forestplot function
  plot_matrix <- rbind(c("", "Difference", "Lower CI", "Upper CI"),
                       cbind(feature_data$concept,
                             feature_data$difference,
                             feature_data$lwr,
                             feature_data$upr))

  # Create the forest plot
  concept_plot_list[[concept]] <- forestplot::forestplot(labeltext = plot_matrix[, 1], 
             mean = as.numeric(plot_matrix[, 2]),
             lower = as.numeric(plot_matrix[, 3]),
             upper = as.numeric(plot_matrix[, 4]),
             xlab = "Difference",
             title = paste0("Forest plot for ", concept))
}

dev.off()
pdf("figures/feature_comparison_mad.pdf")
feature_plot_list$mad
dev.off()
png("figures/feature_comparison_mad.png")
feature_plot_list$mad
dev.off()

feat_ttest_apa <- function(results_df, concept_in, feature_in) {
  # concept_in <- "InteractionContextvoluntary"
  # feature_in  <- "median"

  diff <- results_df %>% 
    filter(concept == concept_in, feature == feature_in) %>% 
    select(difference) %>% 
    pull %>% 
    format(round(., 2), nsmall=2)
  t <- results_df %>% 
    filter(concept == concept_in, feature == feature_in) %>% 
    select(t_value) %>% 
    pull %>% 
    round(., 2) %>% 
    format(., nsmall=2)
  df <- results_df %>% 
    filter(concept == concept_in, feature == feature_in) %>% 
    select(df) %>% 
    pull %>% 
    round(., 2) %>%
    format(., nsmall=2)
  p <- results_df %>% 
    filter(concept == concept_in, feature == feature_in) %>% 
    select(p_value) %>% 
    pull
  p <- ifelse(p < 0.001, "< .001", 
              paste0("= ", format(round(p, 3), nsmall=3)))
  lwr <- results_df %>% 
    filter(concept == concept_in, feature == feature_in) %>% 
    select(lwr) %>% 
    pull %>% 
    round(., 2) %>%
    format(., nsmall=2)
  upr <- results_df %>% 
    filter(concept == concept_in, feature == feature_in) %>% 
    select(upr) %>% 
    pull %>% 
    round(., 2) %>%
    format(., nsmall=2)

  paste("$difference$ = ", diff,
        ", $t$(", df, ") = ", t,
        ", $p$ ", p , 
        ", $95%CI [", lwr,
        ", ", upr, "]",
        sep = "")
}
```

Finally, we can also assess the clusters across other individual difference variables \citep[e.g.,][]{monden2022}. This out-of-feature comparison allows us to check for data artifacts, as well as check whether the developmental clusters are associated with important social markers and individual differences. To illustrate artifact checks, we added the number of ESM measurements into the comparison and find that the participants in the deterioration cluster (cluster 2) on average completed slightly more ESM surveys in general and reported on more intergroup interactions in particular (see $n$ in \fgrref[B]{fig:clusterFeatVar}). In our data exclusion procedures, we ensured that the general time frame and completion rates are similar for all participants and indeed the numbers in ESM measurements generally are largely similar (e.g., see $n$ for well-being and outgroup attitudes). However, the difference in the reported number of interactions might indicate either a clustering artifact or a meaningful difference. The higher average number of interactions in cluster 2 could, for example, indicate a clustering artifact if variances are more inflated due to the larger samples \citep{kogan2006}. In our case this seems less likely because one out of four variables did not differ in terms of the MAD (see \fgrref{fig:cluster_comparison_mad}). At the same time, however, the difference in the number of experienced interactions might also indicate a meaningful difference, where the deteriorating cluster (cluster 2) on average reported more outgroup interactions (`r feat_ttest_apa(results_df, "InteractionContextvoluntary", "n")`), but these interactions were less voluntary (`r feat_ttest_apa(results_df, "InteractionContextvoluntary", "median")`), less meaningful (`r feat_ttest_apa(results_df, "qualityMeaning", "median")`), and less positive (`r feat_ttest_apa(results_df, "qualityOverall", "median")`). Such a finding is in line with past research highlighting the role of negative intergroup interactions in explaining intergroup relations \citep[e.g.,][]{Barlow2012, Prati2021, Graf2014}.

```{=tex}
\begin{figure}[!ht] %hbtp
  \caption{Cluster comparison of Median Absolute Deviation for all variables}
  \label{fig:cluster_comparison_mad}
  \centering\includegraphics[width=\textwidth]{figures/feature_comparison_mad.pdf}
\end{figure}
```

This cluster separation, then, has a number of empirical and practical applications. Firstly, the clusters are descriptive. With tens of variables, hundreds of participants, and thousands of measurements, singular descriptive statistics are often not able to capture the complex patterns that describe the data set. The feature-based clustering offers some direct insight into the complexity within the data set. In our empirical example, we, for example, see that participants are meaningfully distinguished by a combination of high (vs. low) central tendency, variability, and linear trend. Secondly, the clusters identify important groups. The adaptive and deteriorating groups offer starting points for empirical exploration as well as practical interventions. Researchers can start probing what exactly distinguishes the two groups further and generate new bottom-up hypotheses. Practitioners in the resettlement field can use the group separation to identify individuals in need of assistance and can explore contextual factors that might contribute to the difficulties some might face. In our illustration we, for example, found that participants in the deteriorating cluster (cluster 2) reported less need fulfilling interactions over time. Thirdly, the feature-based approach is flexible and meaningful. We were able to use a wide range of time series features that have been central in the ESM literature and were able to use them directly to identify meaningful groups. For our empirical illustration we, among others for example, chose to focus on whether participants differed in their average well-being (i.e., \textit{median}), how much their well-being would vary over time (i.e, \textit{MAD}), and whether their well-being would on average increase or decrease over time (i.e., \textit{linear trend}). Alternatively, for others cyclical patterns might be more important --- for example, whether well-being was higher on weekends. Importantly, in any case, we did not need to translate these dynamic features into probabilistic inference models (e.g., VAR models) to cluster the participants.
